---
title: '**FIVB Beach Volleyball Historic Top 8 Teams Analysis**'
output:
  word_document: default
  html_document:
    df_print: paged
  html_notebook: null
  theme: united
  toc: no
  pdf_document: default
---
### **Tyler Widdison**

  *Evaluation of winning trends related to court and hour for the top 8 FIVB Beach volleyball teams per gender since 2001. The concluding hypothesis is that teams ranked within the top 8 have a higher probability at winning on court 1 at 09:00. Generalized linear model is used in support of the hypothesis. Notes: __^Court records are not kept by FIVB until 2009. ^^Hour records are not kept by FIVB until 2004__*

```{r, include = FALSE}
library(tidyverse)
library(gridExtra)
library(tidyr)
library(ggthemes)
library(viridis)
library(knitr)
library(kableExtra)
library(tidyquant)
library(gridExtra)
library(grid)
library(sm)
library(GGally)
library(stringr)
library(binhf)
library(reshape2)
library(dataMeta)
dfs <- read.csv('all_the_things.csv', header = TRUE, as.is=TRUE,  encoding="UTF-8")
names(dfs)[1] <- 'match_no' #changing the column 1 name
dfs<-dfs[!(dfs$tourn == 'wgoo2001'),] #this tournament is in there under the name 'wbri2001' so I am deleting all of the 'wgoo2001' occurances
dfs$match_no <- suppressWarnings(as.numeric(dfs$match_no)) #needs to be a numeric
dfs$date <- suppressWarnings(as.Date(dfs$date)) #needs to be a date
dfs$court <- suppressWarnings(as.numeric(dfs$court)) #change to numeric 
dfs$result <- NULL #getting rid of result. Score is later down the line
dfs$team_rank <- as.numeric(dfs$team_rank) #needs to be a numeric
dfs$opp_team_rank <- as.numeric(dfs$opp_team_rank) #needs to be a numeric
dfs$duration<-suppressWarnings(as.duration(hms(dfs$duration))) #putting duration into a useable format using lubridate
dfs$duration<-suppressWarnings(as.vector(dfs$duration)) #making the class an integer
dfs$opp_game_three[is.na(dfs$opp_game_three)] <- 0 #ignoring NAs in game three
dfs$team_game_three[is.na(dfs$team_game_three)] <- 0 #...
dfs$tourn_rank[is.na(dfs$tourn_rank)] <- 239 #This NA is only one tournament. I gave it a score of 239 based off teams rankings. 
dfs$score_diff_game_one <-(dfs$team_game_one - dfs$opp_game_one)#score difference for all sets
dfs$score_diff_game_two <-(dfs$team_game_two - dfs$opp_game_two)
dfs$score_diff_game_three <-(dfs$team_game_three - dfs$opp_game_three)
dfs$team_final_score <- (dfs$team_game_one + dfs$team_game_two + dfs$team_game_three) #number of total points scored
dfs$opp_team_final_score <- (dfs$opp_game_one + dfs$opp_game_two + dfs$opp_game_three) #number of total opponent points scored
dfs$team <- str_replace(dfs$team, 'humana-paredes/pavan', 'humana/paredes-pavan') #needing some name changes so things match up properly
dfs$team <- str_replace(dfs$team, 'melissa/pavan', 'humana/paredes-pavan')
dfs$team <- str_replace(dfs$team, 'michon/szczytowicz-kolosinska', 'kolosinska/michon-szczytowicz')
dfs$time <- str_replace(dfs$time, '01:00', '13:00')  #some of the times need adjusting (i checked schedule to make sure this is the case)
dfs$time <- str_replace(dfs$time, '02:00', '14:00')  
dfs$time <- str_replace(dfs$time, '04:00', '16:00')  
dfs$time <- str_replace(dfs$time, '04:57', '16:57')  

#melting the data so I can get both players in a unique setting. Players, at times, will play with different partners throughout one year. Looking at one team wouldn't work for the way I wanted this
df <- melt(dfs, id.vars=c('match_no', 'date', 'time', 'court', 'duration', 'tourn', 'year', 'phase', 'tourn_rank', 'winning_team', 'losing_team', 'gender', 'team', 
                          'team_country', 'team_rank', 'team_match_score', 'team_game_one', 'team_game_two', 'team_game_three', 'opp', 'opp_country', 'opp_match_score', 
                          'opp_game_one', 'opp_game_two', 'opp_game_three', 'opp_team_rank', 'matches_played', 'team_match_won', 'opp_match_won', 'opp_player_1', 
                          'opp_player_2', 'score_diff_game_one', 'score_diff_game_two', 'score_diff_game_three', 'team_final_score', 'opp_team_final_score'))
colnames(df)[which(names(df) == "value")] <- "player" #column changing the melt
df$player <- str_replace(df$player, 'thole j.', 'thole, j.') #more name changes are needing to happen due to data quality needing to be updated
df$player <- str_replace(df$player, 'ces a.', 'cès')
df$player <- str_replace(df$player, 'mol, a.', 'mol a.')

df$team_rank[df$team_rank == 0] <- 150 #Due to time, I only ensured teams 1-50 had a correct ranking. I am giving all other teams with 0 a 150 ranking. 
df$opp_team_rank[df$opp_team_rank == 0] <- 150
df<-df[!is.na(df$team_game_one),] #there are matches with injurys. this throws errors. So I am taking out those injury matches
df$game_three_amount<-lapply(df$team_game_three, function(x){ length(which(x!=0))/length(x)}) #counting the number of set 3s played
df$game_three_amount<-suppressWarnings(as.numeric(df$game_three_amount)) #setting the class as numeric

df$phase2 <- ifelse(grepl("Country", df$phase), 'CQ', #phase of the match is not consistent. For example 'Country Quota BRA' ect ect. I want all Country Quota matches played to say CQ
                    ifelse(grepl("Federation", df$phase), 'CQ',
                           ifelse(grepl("Semi", df$phase), 'Semifinals',
                                  ifelse(grepl("Play-Off", df$phase), 'Playoff',
                                         ifelse(grepl("Gold Medal Match", df$phase), 'Playoff',
                                                ifelse(grepl("Finals", df$phase), 'Final 1st Place',
                                                  ifelse(grepl("Bronze", df$phase), 'Final 1st Place',NA)))))))

df$phase2 <- ifelse(is.na(df$phase2), df$phase, df$phase2) #grouping the phases together so I can get one phase
df$phase <- NULL #I don't want to confuse myself. Nulling out the first phase. 
df<-df %>% rename(phase = phase2)
df$hour <- substring(df$time, 0, 2) #I only want to see hour of each day. Not the Minutes
df$hour<-suppressWarnings(as.integer(df$hour))

all_player_df <- df %>% 
  dplyr::group_by(player, hour, team, team_country, tourn_rank, tourn, date, phase, year, match_no, court, time, team_rank, gender, opp, opp_team_rank) %>% 
  dplyr::summarise(total_matches = sum(matches_played),
                   match_won = sum(team_match_won),
                   match_lost = sum(matches_played - team_match_won),
                   match_win = match_won / (match_won + match_lost),
                   total_set_threes = sum(game_three_amount),
                   total_sets_played = (total_matches + total_matches + total_set_threes),
                   rank = sum(team_rank))

all_player_df$total_matches<-suppressWarnings(as.character(all_player_df$total_matches))

all_player_df$total_matches <- str_replace(all_player_df$total_matches, '2', '1')

all_player_df$total_matches <- suppressWarnings(as.integer(all_player_df$total_matches))

df_men <- all_player_df %>%
  dplyr::filter(gender == 'm' & team_rank <= 8)

df_women <- all_player_df %>%
  dplyr::filter(gender == 'w' & team_rank <= 8)
```


  # Mean of matches played and won from the top 8 teams considering 2001 - 2019.

### **Men**
#### There has been a downward trend of top 8 mens teams playing matches per year with 2017 being the lowest. Avg matches played for mens top 8 in a FIVB season is 57.59 and wins is 41.04 from 2001 - 2019. 
```{r, echo = FALSE, error=TRUE}
t <- df_men %>%
  dplyr::group_by(player, year) %>%
  dplyr::summarise(total_matches = sum(total_matches),
                   total_wins = sum(match_won))
t2.1 <- t %>%
  dplyr::filter(total_matches > 29)

t2.12<-melt(t2.1, id.vars = c('year', 'player'))
t2.12$player <- NULL

#plot1#
ggplot(data=t2.12, aes(x=value, group=variable, fill=variable)) +
  geom_density(adjust=1.5, alpha = 0.6) + 
  geom_vline(xintercept = 57.59, linetype = 'dotted', size = 1.5, color = '#9c5959') +
  geom_vline(xintercept = 41.04, linetype = 'dotted', size = 1.5, color = '#50948a') + 
  labs(title = 'Density of mens matches played and won 2001-2019',
       y = 'Density',
       x = 'Matches') + 
  scale_fill_discrete(name = '',
                      labels = c('Matches played','Matches won'))

t3<-t %>%
  dplyr::group_by(year) %>%
  dplyr::filter(total_matches > 29) %>%
  dplyr::summarise(total_matches = sum(total_matches),
                   total_wins = sum(total_wins))

#plot2#
ggplot(t3)+
  geom_line(aes(year, total_matches)) + 
  geom_point(aes(x = year, y = total_matches, color = 'red'), size = 3.5, alpha = 0.5) + 
  geom_smooth(aes(x = year, y = total_matches),color = 'red', se = F) +
  geom_line(aes(year, total_wins)) + 
  geom_point(aes(x = year, y = total_wins, color = 'blue'), size = 3.5, alpha = 0.5)+
  geom_smooth(aes(x = year, y = total_wins), se = F) +
  labs(title = 'Mens matches played & won', color = '', x = 'Year' , y= 'Matches')+
  scale_color_manual(labels = c("Matches won", "Matches played"), values = c("blue", "red")) +
  scale_x_continuous(breaks = seq(2001, 2019, by = 1)) + 
  scale_y_continuous(breaks = seq(450, 1250, by = 50)) +
  theme_tq() 

```




### **Women**
#### There has been a slight downward trend of top 8 womens teams playing matches per year with the lowest being 2004. The avg matches played for womens top 8 in a FIVB season is 59.8 and matches won 43.54 from 2001 - 2019.
```{r, echo = FALSE, error=TRUE}
d <- df_women %>%
  dplyr::group_by(player, year) %>%
  dplyr::summarise(total_matches = sum(total_matches),
                   total_wins = sum(match_won))
d2 <- d %>%
  dplyr::filter(total_matches > 29)


d2<-melt(d2, id.vars = c('year', 'player'))
d2$player <- NULL



#plot1#
ggplot(data=d2, aes(x=value, group=variable, fill=variable)) +
  geom_density(adjust=1.5, alpha = 0.6) + 
  geom_vline(xintercept = 59.8, linetype = 'dotted', size = 1.5, color = '#9c5959') +
  geom_vline(xintercept = 43.54, linetype = 'dotted', size = 1.5, color = '#50948a') +
  labs(title = 'Density of womens matches played and won 2001-2019',
       y = 'Density',
       x = 'Matches') + 
  scale_fill_discrete(name = '',
                      labels = c('Matches played','Matches won'))

d3<-d %>%
  dplyr::group_by(year) %>%
  dplyr::filter(total_matches > 29) %>%
  dplyr::summarise(total_matches = sum(total_matches),
                   total_wins = sum(total_wins))

#plot2#
ggplot(d3)+
  geom_line(aes(year, total_matches)) + 
  geom_point(aes(x = year, y = total_matches, color = 'red'), size = 3.5, alpha = 0.5) + 
  geom_smooth(aes(x = year, y = total_matches),color = 'red', se = F) +
  geom_line(aes(year, total_wins)) + 
  geom_point(aes(x = year, y = total_wins, color = 'blue'), size = 3.5, alpha = 0.5)+
  geom_smooth(aes(x = year, y = total_wins), se = F) +
  labs(title = 'Womens matches played & won', color = '', x = 'Year' , y= 'Matches')+
  scale_color_manual(labels = c("Matches won", "Matches played"), values = c("blue", "red")) +
  scale_x_continuous(breaks = seq(2001, 2019, by = 1)) + 
  scale_y_continuous(breaks = seq(420, 1250, by = 50)) +
  theme_tq() 


```


# Courts match's were played by a team in the top 8.
### **Men**
#### Matches played and matches won per court 2009 - 2019. Top 8 teams have the highest winning percentage on court 5 and 3. Court 1 has the lowest winning percentage. 
```{r, echo = FALSE, error=TRUE}
c <- df_men %>%
  dplyr::group_by(court, year) %>%
  dplyr::summarise(total_matches = sum(total_matches),
                   total_win = sum(match_win),
                   match_lost = sum(match_lost),
                   match_win_perce = total_win /total_matches )

c <- na.omit(c)

c <- c%>% dplyr::filter(total_matches >= 30)

ggplot(c, aes(x = year, y = total_matches, colour = factor(court))) +
  geom_point(size = 2) + 
  geom_line(alpha = 0.7) +
  labs(x = 'Year', 
       y = 'Matches',
       colour = 'Court',
       title = 'Top 8 mens matches per court per year') + 
  scale_x_continuous(breaks = 2009:2019) + 
  scale_y_continuous(breaks = seq(0, 450, by = 25))

c2<-c %>% 
  dplyr::group_by(court) %>% 
  dplyr::summarise(total_matches = sum(total_matches),
                   total_win = sum(total_win),
                   match_win_perce = total_win / total_matches)


ggplot(c2, aes(court, total_matches)) + 
  geom_col(aes(court, total_matches), color = 'green', fill = 'lightgreen') +
  geom_text(aes(label = formattable::percent(match_win_perce)), nudge_y = 145, alpha = 0.5) + 
  geom_text(aes(label = total_matches),nudge_y = -145, alpha = 0.5) + 
  scale_x_continuous(breaks = 1:6) + 
  labs(title = 'Mens win % and matches played per court',
       x = 'Court',
       y = 'Matches')

```


### **Women**
#### Matches played on court by womens top 8 teams 2009 - 2019. Top 8 teams have the highest winning percentage on court 5, 3 and 4. Court 1 has the lowest winning percentage. 
```{r, echo = FALSE, error=TRUE}
k <- df_women %>%
  dplyr::group_by(court, year) %>%
  dplyr::summarise(total_matches = sum(total_matches),
                   total_win = sum(match_win),
                   match_lost = sum(match_lost),
                   match_win_perce = total_win /total_matches )

k <- na.omit(k)

k <- k%>% dplyr::filter(total_matches >= 30)

ggplot(k, aes(x = year, y = total_matches, colour = factor(court))) +
  geom_point() + 
  geom_line() +
  labs(x = 'Year', 
       y = 'Matches',
       colour = 'Court',
       title = 'Top 8 womens matches per court per year') + 
  scale_x_continuous(breaks = 2009:2019) + 
  scale_y_continuous(breaks = seq(0, 450, by = 25))

k2<-k %>% 
  dplyr::group_by(court) %>% 
  dplyr::summarise(total_matches = sum(total_matches),
                   total_win = sum(total_win),
                   match_win_perce = total_win / total_matches)


ggplot(k2, aes(court, total_matches)) + 
  geom_col(aes(court, total_matches), color = 'green', fill = 'lightgreen') +
  geom_text(aes(label = formattable::percent(match_win_perce)), nudge_y = 145, alpha = 0.5) + 
  geom_text(aes(label = total_matches),nudge_y = -145, alpha = 0.5) + 
  scale_x_continuous(breaks = 1:6) +
  labs(title = 'Womens win % and matches played per court',
     x = 'Court',
     y = 'Matches')

```

# Hour of day match's were played by a team in the top 8.
### **Men**
#### Matches played by hour by mens teams in top 8 from 2004-2019. The lowest winning percentage by a team in the top 8 is 21:00. And the highest is at 08:00.
```{r, echo = FALSE, error=TRUE}
h <- df_men %>%
  dplyr::group_by(hour) %>%
  dplyr::summarise(total_matches = sum(total_matches),
                   total_win = sum(match_win),
                   match_lost = sum(match_lost),
                   match_win_perce = total_win /total_matches )

h <- na.omit(h)

h <-h%>% dplyr::filter(total_matches >= 31)

ggplot(h, aes(hour, total_matches)) + 
  geom_col(aes(hour, total_matches), color = 'green', fill = 'lightgreen') +
  geom_text(aes(label = formattable::percent(match_win_perce)), nudge_y = 145, alpha = 0.5) + 
  geom_text(aes(label = total_matches),nudge_y = -145, alpha = 0.5) + 
  scale_x_continuous(breaks = 8:22) + 
  theme_tq() +
  labs(title = 'Mens win % and matches played per hour',
     x = 'Hour',
     y = 'Matches')
```

### **Women**
#### Matches played by hour by womens teams in top 8 from 2009-2019. The lowest winning percentage by a team in the top 8 is 22:00. And the highest is at 08:00.
```{r, echo = FALSE, error=TRUE}
a <- df_women %>%
  dplyr::group_by(hour) %>%
  dplyr::summarise(total_matches = sum(total_matches),
                   total_win = sum(match_win),
                   match_lost = sum(match_lost),
                   match_win_perce = total_win /total_matches )

a <- na.omit(a)
  
a <-a%>% dplyr::filter(total_matches >= 31)

ggplot(a, aes(hour, total_matches)) + 
  geom_col(aes(hour, total_matches), color = 'green', fill = 'lightgreen') +
  geom_text(aes(label = formattable::percent(match_win_perce)), nudge_y = 145, alpha = 0.5) + 
  geom_text(aes(label = total_matches),nudge_y = -145, alpha = 0.5) + 
  scale_x_continuous(breaks = 8:22) + 
  theme_tq() +
  labs(title = 'Womens win % and matches played per hour',
     x = 'Hour',
     y = 'Matches')
```


# Match win % per hour and court trend by mens teams in top 8 from 2009-2019.
### **Men**
#### This data only takes into account when the court and time were present. The highest winning % is court 5 at 12:00. The lowest winning % is court 1 at 20:00.
```{r, echo = FALSE, error=TRUE}
d <- df_men %>%
  dplyr::group_by(hour, court) %>%
  dplyr::summarise(total_matches = sum(total_matches),
                   win_percent = sum(match_won) / total_matches)
d <- na.omit(d, echo=FALSE)
  
d <-d%>% dplyr::filter(total_matches >= 29)

d$total_matches <- NULL
d2<-melt(d, id.vars = c('court', 'hour'))

#ggplot(d, aes(hour, win_percent, size = court, fill = factor(court))) + 
#  geom_point(alpha = 0.5, color = 'black', shape = 22, size = 8) + 
#  scale_size(range = c(3, 8), name = 'court', guide = F)  +
#  scale_x_continuous(breaks = 08:22) + 
#  scale_y_reverse(labels = scales::percent) +
#  guides(fill = guide_legend(override.aes = list(size=10))) + 
#  scale_fill_discrete('Court') + 
#  labs(title = 'Win % according to court and hour',
#       y= 'Win %',
#       x = 'Hour')

ggplot(d2, aes(x = hour, y = value, colour = factor(court))) +
  geom_point(size = 2, alpha = 0.8) + 
  geom_line(size = 1, alpha = 0.5) +
  labs(x = 'Hour', 
       y = 'Win%',
       colour = 'Court',
       title = 'Top 8 mens win% per court per hour') + 
  scale_x_continuous(breaks = 08:22) + 
  scale_y_continuous(labels = scales::percent)

```

### **Women**
#### This data only takes into account when the court and time were present. The highest winning % is court 5 at 09:00 and 12:00. The lowest winning % is court 1 at 20:00.
```{r, echo = FALSE, error=TRUE}
da <- df_women %>%
  dplyr::group_by(hour, court) %>%
  dplyr::summarise(total_matches = sum(total_matches),
                   win_percent = sum(match_won) / total_matches)

da <- na.omit(da)
  
da <- da%>% dplyr::filter(total_matches >= 29)

da$total_matches <- NULL
da2<-melt(da, id.vars = c('court', 'hour'))

#ggplot(da, aes(hour, win_percent, size = court, fill = factor(court))) + 
#  geom_line(alpha = 0.5) + 
#  scale_size(range = c(3, 8), name = 'court', guide = F)  +
#  scale_x_continuous(breaks = 08:22) + 
#  scale_y_reverse(labels = scales::percent) +
#  guides(fill = guide_legend(override.aes = list(size=10))) + 
#  scale_fill_discrete('Court') + 
#  labs(title = 'Win % according to court and hour',
#       y= 'Win %',
#       x = 'Hour')

ggplot(da2, aes(x = hour, y = value, colour = factor(court))) +
  geom_point(size = 2, alpha = 0.8) + 
  geom_line(size = 1, alpha = 0.5) +
  labs(x = 'Hour', 
       y = 'Win%',
       colour = 'Court',
       title = 'Top 8 womens win% per court per hour') + 
  scale_x_continuous(breaks = 08:22) + 
  scale_y_continuous(labels = scales::percent)

```



# Probability of winning by court and hour using Generalized linear regression.
### **Men**
#### The highest probability for a men's team to win in the top 8 is court 5 at 11:00. With the loweset being at 21:00 on court 1.


```{r, echo = FALSE, error=TRUE}
f <- df_men %>%
  dplyr::group_by(hour, court) %>%
  dplyr::summarise(total_matches = sum(total_matches),
                   match_win_perce = sum((match_won) / total_matches))

f <- na.omit(f)
f <- f %>% dplyr::filter(total_matches >= 29)

formula <- match_win_perce ~hour + court

mhlm <- glm(formula, data=f)
prob <- predict(mhlm, newdata=f, type="response")
prob <- round(prob,3)
f$prob <- prob


#f %>%
#  arrange(desc(prob)) %>%
#  mutate(court = factor(court, court)) %>%
#  ggplot(aes(x=prob, y=match_win_perce, size=total_matches, color=court)) +
#  geom_point(alpha=0.5) +
#  scale_size(range = c(.1, 15)) + 
#  scale_y_reverse()



f %>%
  ggplot(aes(court, hour)) +
  geom_point(aes(color = prob), size = 7, alpha = 0.5) + 
  scale_size(range = c(.5, 9)) +
  scale_y_continuous(breaks = seq(8, 22, by = 1)) +
  labs(title = 'FIVB mens top 8 team probability of winning by court and hour',
       subtitle = 'Data from 2009 - 2019',
       size = 'Porbability',
       color ='Probability',
       x = 'Court',
       y = 'Hour')+
  scale_color_viridis(option="C")+
  scale_x_continuous(breaks = 1:6) 

f$prob<-format(round(f$prob,3))
f$match_win_perce <- NULL
f$total_matches <- NULL

f<-f[order(-prob),]
colnames(f) <- c('Hour', 'Court', 'Probablity')
kable(f) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = 'left', fixed_thead = T) %>%
  scroll_box(width = '200px', height='500px')

#kable(ft) %>%
#  kable_styling(bootstrap_options = "striped", full_width = F, position = 'center', fixed_thead = T)
#$qqnorm(f$prob, pch = 1, frame = FALSE)
#$qqline(f$prob, col = "steelblue", lwd = 2)


```



### **Women**
#### The highest probability for a women's team to win in the top 8 is court 5 at 09:00. With the loweset being at 21:00 on court 1.
```{r, echo = FALSE, error=TRUE}
f2 <- df_women %>%
  dplyr::group_by(hour, court) %>%
  dplyr::summarise(total_matches = sum(total_matches),
                   match_win_perce = sum((match_won) / total_matches))

f2 <- na.omit(f2)
f2 <- f2 %>% dplyr::filter(total_matches >= 29)

formula <- match_win_perce ~hour + court

mhlm2 <- glm(formula, data=f2)
prob2 <- predict(mhlm2, newdata=f2, type="response")
prob2 <- round(prob2,3)
f2$prob2 <- prob2


#f2 %>%
#  arrange(desc(prob2)) %>%
#  mutate(court = factor(court, court)) %>%
#  ggplot(aes(x=prob2, y=match_win_perce, size=total_matches, color=court)) +
#  geom_point(alpha=0.5) +
#  scale_size(range = c(.1, 15)) + 
#  scale_y_reverse()



f2 %>%
  ggplot(aes(court, hour)) +
  geom_point(aes(color = prob2), size = 7, alpha = 0.5) + 
  scale_size(range = c(.5, 9)) +
  scale_y_continuous(breaks = seq(8, 22, by = 1)) +
  labs(title = 'FIVB womens top 8 team probability of winning by court and hour',
       subtitle = 'Data from 2009 - 2019',
       size = 'Probability%',
       color ='Probability',
       x = 'Court',
       y = 'Hour')+
  scale_color_viridis(option="C")+
  scale_x_continuous(breaks = 1:6) 

f2$prob2<-format(round(f2$prob2,3))
f2$match_win_perce <- NULL
f2$total_matches <- NULL

f2<-f2[order(-prob2),]
colnames(f2) <- c('Hour', 'Court', 'Probablity')
kable(f2) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = 'left', fixed_thead = T) %>%
  scroll_box(width = '200px', height='500px')

#qqnorm(f2$prob2, pch = 1, frame = FALSE)
#qqline(f2$prob2, col = "steelblue", lwd = 2)

```

### *Conclusion*
#### There is an apparent trend of teams in the top 8 winning more and having higher probility of winning on lower courts earlier in the day. And lower probility later in the day on higher courts. This trend is likely due to teams in the top 8 advancing further into tournaments and playing other teams in the top 8. 
